---
title: "Text Analysis and Spatial Data for Economists"
subtitle: "Assignment 2"
author: Haoyu Yang
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  toc: yes
toc_float: true
toc_collapsed: true
--- 

```{r setup, include=T , message = F}
library(raster)
library(dplyr) 
library(leaflet)
library(rmapshaper) 
library(RColorBrewer) 
library(mapview) 
library(sf) 
library(spData) 
library(ggplot2) 
library(rstudioapi)
library(gridExtra)
library(magrittr) 
```



```{r, eval = FALSE, include = FALSE}
# clean working environment
rm(list = ls())
```


# Raster data

## Getting raster data

For this assignment, we will use the municipality boundary and the housing price data we have already used in the last assignment. 

```{r}
# Load here municipality boundary and housing prices from the previous assignment
setwd("~/Documents/forth_semester/text")
hp <- st_read("./hp_small.csv", 
  options = c("X_POSSIBLE_NAMES=longitude2", "Y_POSSIBLE_NAMES=latitude2"), 
  stringsAsFactors = FALSE, 
  crs = 4326 
)
municipality_bound <- st_read("data/raw/Swiss boundary/swissBOUNDARIES3D_1_5_TLM_HOHEITSGEBIET.shp")

```


We will complement these data with two raster datasets:

+ Visit [https://www.swisstopo.admin.ch/en/geodata/height.html](https://www.swisstopo.admin.ch/en/geodata/height.html) and download the *Digital Height Model 25/200* for Switzerland.

  + Read the file `DHM200.xyz` as a raster. Check its CRS and assign a value if needed. If this information is missing, retrieve the relevant CRS in the documentation and assign to your object using the function `crs(x) <- value`. Use an EPSG code as a `proj4string` definition with `"+init=epsg:MY_NUMBER"` (so the command is:  `crs(x) <- "+init=epsg:MY_NUMBER"`). You will probably get warnings while assigning the CRS. This is due to a migration from `proj4string` towards `PROJ6` standards. You can ignore these warnings.


```{r}
# Load the file DHM200.xyz from the Digital Height Model 25/200 for Switzerland
# Assign the correct CRS if needed

raster_DHM <- raster("DHM200.xyz")

crs(raster_DHM) <- "+init=epsg:21781"

mapview(raster_DHM)

```

+ Visit [https://map.geo.admin.ch](https://map.geo.admin.ch) and downloard the daytime road traffic noise exposure from the Federal Office for the Environment.
  
  + Read the file `StrassenLaerm_Tag.tif` (that is in the folder `STRASSENLAERM_Tag` that you downloaded) as a raster. Check its CRS and assign a value if needed.

```{r}
# Load the file StrassenLaerm_Tag.tif
raster_Strassen <- raster("StrassenLaerm_Tag.tif")
crs(raster_Strassen)
```


## Raster extraction

+ Assign to the housing price data the level of noise exposure for that location. 

```{r}
# Step 1: reproject the vector object to the CRS of the raster data
hp <- st_transform(hp, crs(raster_Strassen))

# Step 2: extract the values for the corresponding raster's cell
hp$noise_level <-raster::extract(raster_Strassen, hp)
mapview(hp, zcol = "noise_level")
```


## Rasterization

+ Rasterize the dataset on housing prices to show the average price per square meters (`a_brutm_m2`) for grids of 1,000m x 1,000m 
  + Create a raster template using housing price data. 
  + Convert (`a_brutm_m2`) into numeric using the functions `as.numeric(as.character(x))`

```{r}
# Convert factor variable into numeric
hp$a_brutm_m2 <- as.numeric(as.character(hp$a_brutm_m2))
# Create raster template
ras_temp <- raster(extent(hp), resolution = c(1000, 1000))
# Rasterize 
price_raster <- rasterize(hp, ras_temp, field = "a_brutm_m2", fun = mean)
# Plot
plot(price_raster, main = "Average Price per square meter (1000x1000m)")
```

## Spatial vectorization

+ Create contour lines for 250, 500, 1000 and 2000 m.a.s.l for the digital height model. Use a mask to select only the data for Switzerland.
  + Create a polygon for Switzerland based on the municipality boundary data. Remove the z geometry using `st_zm()` and reproject the data.
  + Store the polygon as `Spatial` object (with `as(x,"Spatial")`).
  + Create a mask for the the raster data
  + Create contour lines for the desired levels (look at `?rasterToContour` to create the desired lines).

```{r}
# Create a polygon for Switzerland
swiss_bound <- municipality_bound %>% 
  st_union() %>%          
  st_zm() %>%             
  st_transform(crs(raster_DHM))  
swiss_bound_sp <- as(swiss_bound, "Spatial")
# Create a mask for raster data
dhm_mask <- mask(raster_DHM, swiss_bound_sp)
# Create contour lines
contours <- rasterToContour(dhm_mask, levels = c(250, 500, 1000, 2000))
mapview(contours)
```

+ Create a hillshade layer to use as a basemap for the noise data

```{r}
# Create a hill shade layer and mask cells outside Switzerland
slope <- terrain(dhm_mask, opt = "slope")
aspect <- terrain(dhm_mask, opt = "aspect")
hill <- hillShade(slope, aspect)
hill_mask <- mask(hill, swiss_bound_sp)
# Plot hill shade and noise data
mapview(hill_mask, layer.name = "Hill") + 
  mapview(hp, zcol = "noise_level", layer.name = "Noise Level")


```

